### 2022-10-31 README.Rmd
Added more functions to aid comparing scenarios. No EWN

* 2022-10-18 aMSE 0.0.18 In the projections relicates across years has now been changed to years across replicates to allow for inclusion of FIS performance measures. Also, further comparison functions included.

>>>>

* 2022-10-31 aMSE 0.0.20 added do_comp_outputs, scenebyvar, scenebyzone, projectiononly, and sauquantbyscene to assist with comparing scenarios.

* 2022-10-26 aMSE 0.0.19 added more functions to facilitate comparing scenarios.

* 2022-10-18 aMSE 0.0.18 In the projections replicates across years has now been changed to years across replicates to allow for inclusion of FIS performance measures. Also, further comparison functions included.
